Exploratory analysis

### 2023-04-27 code/analysis_code/exploratory_analysis.qmd
add review from Weifan Wu

# Setup

```{r, warning=FALSE, message=FALSE}
library(here) #for data loading/saving
library(dplyr)
library(ggplot2)
library(haven)
library(gridExtra) # To combine plots
library("gtsummary") # For producing table 1
#library("kableExtra") # For producing a nice table 1
```

>>>>

# Setup
```{r, warning=FALSE, message=FALSE}
library(here) #for data loading/saving
library(dplyr)
library(ggplot2)
library(haven)
library(gridExtra) # To combine plots
library(gtsummary) # For producing table 1
#library("kableExtra") # For producing a nice table 1
```
